Raman sideband cooling of a single sodium atom to 3D ground state

### 2017-04-19 presentations/2017-04-19_itamp/present.tex
[presentations/2017-04-19_itamp] Tweaks after practice talk

\title[Na ground state cooling]{Raman sideband cooling of single sodium atom to 3D ground state}
\date{April 19, 2017}
\author[Yichao Yu]{Yichao Yu\\
  \vspace{0.5cm}
  {\footnotesize Lee Liu, Dr. Nick Hutzler,\\
    Jessie Zhang, Dr. Jon Hood}}
\institute{Ni Group/Harvard}

@@

\begin{frame}{}
  \begin{center}
    \begin{tikzpicture}
      \visible<1> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_full_min.png}};
      }
      \visible<2-> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_trap_min.png}};
      }
      \visible<3-> {
        \path (3, -3) node
        {\includegraphics[width=3cm]{../../experiments/nacs_atoms/imgs/single_viridis.png}};
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Wave function size}
  \begin{center}
    \begin{tikzpicture}
      \shade[ball color=blue!90] (0, 0) circle (0.45);
      \shade[ball color=orange!90] (0.4, 0.2) circle (0.3);
      \draw[<->,line width=1] (-0.45, 0.4) -- (0.35, 0.8);
      \path (-0.05, 0.6) node[rotate=26.565,above=2pt] {$4a_0$};
      \path (0.2, -2) node[below] {\textbf{Molecule}};

      \draw[line width=1] plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {(\x)^2 * 0.8 - 1.5});
      \draw[line width=2,orange!90!black]
      plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {exp(-(\x)^2 * 1.3) - 0.988});
      \draw[line width=0.8] (6 - 0.8, -0.988) -- (6 + 0.8, -0.988);
      \draw[<->,line width=1] (6 - 1, 0.3) -- (6 + 1, 0.3);
      \path (6, 0.3) node[above] {$1000a_0$};
      \path (6, -2) node[below] {\textbf{Atom}};
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Raman sideband cooling of Sodium}
  \begin{columns}
    \column{6.5cm}
    \includegraphics[width=6cm]{Na_RSC_schematic.pdf}
    \column{5cm}
    \visible<2->{
      \begin{block}{Difficulties}
        \begin{itemize}
        \item High initial temperature ($40\mu K$)
        \item<3-> High recoil heating
        \end{itemize}
      \end{block}
    }
  \end{columns}
\end{frame}

\begin{frame}{Cooling sequence}
  \tikzfading[name=fade img right,
  left color=transparent!90, right color=transparent!0]
  \begin{tikzpicture}[scale=0.75]
    % 0.0 - 1.5 axial
    % 1.5 - 2.0 OP
    % 2.0 - 3.5 axial
    % 3.5 - 4.0 OP
    % 4.0 - 5.0 radial 2
    % 5.0 - 5.5 OP
    % 5.5 - 7.0 axial
    % 7.0 - 7.5 OP
    % 7.5 - 9.0 axial
    % 9.0 - 9.5 OP
    % 9.5 - 10.5 radial 3
    % 10.5 - 11.0 OP

    %% Pulse mark
    \foreach \i in {2.0, 4.0, 5.5, 7.5, 9.5, 11.0, 13.0, 15.0, 16.5, 18.5, 20.5} {
      \draw[gray!20, line width=1.5] (\i, 1.8) -- (\i, -6.0);
    }

    %% Axial
    \foreach \i in {0, 5.5, 11.0, 16.5} {
      \fill[blue!30]
      plot[draw,samples=200,domain=\i:{\i+1.5},variable=\x] ({\x}, {sin((\x-\i) * 120)^4})
      -- cycle;
      \path (\i+1, 1) node[above,blue,align=center] {$n$-th\\order};
      \fill[blue!30]
      plot[draw,samples=200,domain={\i+2.0}:{\i+3.5},variable=\x] ({\x}, {sin((\x-\i-2.0) * 120)^4})
      -- cycle;
      \path (\i+3, 1) node[above,blue,align=center] {$(n-1)$-th\\order};
      \draw[line width=1,blue] plot[domain=\i:{\i+1.5},variable=\x]
      ({\x}, {sin((\x-\i) * 120)^4}) -- (\i+2.0, 0)
      plot[domain={\i+2.0}:{\i+3.5},variable=\x]
      ({\x}, {sin((\x-\i-2.0) * 120)^4})-- (\i+5.5, 0);
    }
    \path (0, 0.5) node[left,blue,align=center] {\textbf{Axis 1}\\\textit{Axial}};

    %% Radial 2
    \foreach \i in {0, 11.0} {
      \fill[red!30]
      plot[draw,samples=200,domain={\i+4.0}:{\i+5.0},variable=\x] ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2})
      -- cycle;
      \draw[line width=1,red] (\i, -2) -- plot[domain={\i+4.0}:{\i+5.0},variable=\x]
      ({\x}, {1.5*sin((\x-\i-4.0) * 180)^4 - 2}) -- (\i+11.0, -2);
    }
    \path (0, -1.5) node[left,red,align=center] {\textbf{Axis 2}\\\textit{Radial}};

    %% Radial 3
    \foreach \i in {0, 11.0} {
      \fill[black!30]
      plot[draw,samples=200,domain={\i+9.5}:{\i+10.5},variable=\x] ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4})
      -- cycle;
      \draw[line width=1,black] (\i, -4) -- plot[domain={\i+9.5}:{\i+10.5},variable=\x]
      ({\x}, {1.5*sin((\x-\i-9.5) * 180)^4 - 4}) -- (\i+11.0, -4);
    }
    \path (0, -3.5) node[left,black,align=center] {\textbf{Axis 3}\\\textit{Radial}};

    %% OP
    \foreach \i in {0, 5.5, 11.0, 16.5} {
      \filldraw[fill=orange!30,draw=orange,line width=1.5]
      (\i+1.5, -6) -- (\i+1.5, -4.5) -- (\i+2.0, -4.5) -- (\i+2.0, -6) -- cycle;
      \filldraw[fill=orange!30,draw=orange,line width=1.5]
      (\i+3.5, -6) -- (\i+3.5, -4.5) -- (\i+4.0, -4.5) -- (\i+4.0, -6) -- cycle;
      \filldraw[fill=orange!30,draw=orange,line width=1.5]
      (\i+5.0, -6) -- (\i+5.0, -4.5) -- (\i+5.5, -4.5) -- (\i+5.5, -6) -- cycle;
    }
    \path (0, -5.5) node[left,orange,align=center] {\textbf{Optical}\\\textbf{pumping}};
    \draw[line width=2,orange] (0,-6) -- (23,-6);

    %% Cycle mark
    \draw[decoration={brace,mirror,raise=3pt, amplitude=10pt},decorate,line width=2]
    (0,-6) -- node[below=15pt] {\scalebox{1.5}{One cooling cycle}} (11,-6);

    \fill[white,path fading=fade img right] (11, -7) rectangle (14.5, 2.5);
    \fill[white,path fading=fade img right] (11, -7) rectangle (14.5, 2.5);
    \fill[white] (14.5, 2.5) rectangle (23, -7);

    \draw[line width=2,orange,->] (0,-6) -- (12,-6) node[right, below] {\scalebox{2}{$t$}};
  \end{tikzpicture}
\end{frame}

\begin{frame}{Raman sidebands}
  \begin{tikzpicture}
    \visible<1-2> {
      \path (1.75, 4) node {
        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
      };
      \path (0, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
      };
      \path (6, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3_before.png}
      };
      \visible<2> {
        \draw[red, <-, line width=1.5] (-1.4, 4.5) -- (-1.2, 5.2)
        node[above right] {1st order heating};
        \draw[<-, line width=1.5] (-0.7, 4.2) -- (-0.5, 4.8) node[above right] {Carrier};
        \draw[black!40!green, <-, line width=1.5] (0.05, 4.2) -- (0.2, 4.6)
        node[right] {1st order cooling};
        \draw[blue, <-, line width=1.5] (0.8, 3.9) -- (1.2, 4.1)
        node[right] {2nd order cooling};
        \path[magenta] (2, 3.5) node[right] {And higher orders{$\cdots$}};

        \draw[<-, line width=1.5] (-0.35, 0) -- (0, 0.8) node[right] {Carrier};

        \draw[<-, line width=1.5] (5.67, 0.1) -- (6, 0.8) node[right] {Carrier};
      }
    }
    \visible<3-> {
      \path (1.75, 4) node {
        \includegraphics[width=8.5cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
      };
      \path (0, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
      };
      \path (6, 0) node {
        \includegraphics[width=5cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
      };
    }
    \visible<4-> {
      \path[blue] (2, 4.6) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{93.1(2.5)\%}$};
      \path[blue] (2, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{91.9(2.3)\%}$};
      \path[blue] (8, 0.1) node[fill=white,opacity=0.6,text opacity=1,align=center]
      {$\bm{P_{ground\ state}}$\\$\bm{92.9(2.5)\%}$};
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \fill[white,path fading=fade img right] (4, 2.1) rectangle (7, 6);
      \path (4, 4) node[fill=blue!80!white,opacity=0.8,text opacity=1,
      text=white!90!yellow,right,align=center,
      rounded corners=0.2cm,inner sep=0.2cm] {
        \textbf{3D ground state:} $79.5(3.6)\%$\\
        \textbf{Loss after cooling:} $15\%$\\\\
        \textbf{Total 3D ground state}\\
        \textbf{preparation fidelity}\\
        $67.6(3.1)\%$
      };
    }
  \end{tikzpicture}
\end{frame}

\begin{frame}{Rabi flopping (radial)}
  \begin{center}
    \visible<+->{
      \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}\\
    }
    \visible<+->{
      Good agreement between spectrum and Rabi flopping data.
    }
  \end{center}
\end{frame}

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}\\
    Decoherence caused by magnetic field fluctuation.
  \end{center}
\end{frame}

>>>>

\title[Na ground state cooling]{Raman sideband cooling of a single sodium atom to 3D ground state}
\date{April 19, 2017}
\author[Yichao Yu]{Yichao Yu\\
  \vspace{0.5cm}
  {\footnotesize Lee Liu, Dr. Nick Hutzler,\\
    Jessie Zhang, Dr. Jon Hood}}
\institute{Ni Group/Harvard}

@@

\begin{frame}{}
  \begin{center}
    \begin{tikzpicture}
      \visible<1> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_full_min.png}};
      }
      \visible<2-> {
        \path (0, 0) node
        {\includegraphics[width=10cm]{../2015-05-05_cua/overall_trap_min.png}};
        \path (3, -3) node
        {\includegraphics[width=3cm]{../../experiments/nacs_atoms/imgs/single_viridis.png}};
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Wave function size mismatch}
  \begin{center}
    \begin{tikzpicture}
      \shade[ball color=blue!90] (0, 0) circle (0.45);
      \shade[ball color=orange!90] (0.4, 0.2) circle (0.3);
      \draw[<->,line width=1] (-0.45, 0.4) -- (0.35, 0.8);
      \path (-0.05, 0.6) node[rotate=26.565,above=2pt] {$4a_0$};
      \path (0.2, -2) node[below] {\textbf{Molecule}};

      \draw[line width=1] plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {(\x)^2 * 0.8 - 1.5});
      \draw[line width=2,orange!90!black]
      plot[samples=200,domain=-2:2,variable=\x] ({\x + 6}, {exp(-(\x)^2 * 1.3) - 0.988});
      \draw[line width=0.8] (6 - 0.8, -0.988) -- (6 + 0.8, -0.988);
      \draw[<->,line width=1] (6 - 1, 0.3) -- (6 + 1, 0.3);
      \path (6, 0.3) node[above] {$1000a_0$};
      \path (6, -2) node[below] {\textbf{Atom}};
    \end{tikzpicture}
    \vspace{1cm}
    \begin{block}{Goal of cooling}
      \begin{itemize}
      \item Single initial state
      \item Shrink wavefunction size
      \end{itemize}
    \end{block}
  \end{center}
\end{frame}

\begin{frame}{Raman sideband cooling of Sodium}
  \begin{columns}
    \column{6.5cm}
    \includegraphics[width=6cm]{Na_RSC_schematic.pdf}
    \column{5cm}
    \visible<2->{
      \begin{block}{Difficulties}
        \begin{itemize}
        \item High initial temperature ($40\mu K$)
        \item<3-> High recoil heating\\
          {\footnotesize (High Lamb Dicke parameter)}
        \end{itemize}
      \end{block}
    }
  \end{columns}
\end{frame}

\begin{frame}{Raman sidebands}
  \begin{center}
    \begin{tikzpicture}
      \visible<1> {
        \path (0, 0) node {
          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2_before.png}
        };
        \draw[<-, line width=1.5] (-0.7, 0) -- (0, 1.6) node[right] {\Large Carrier};
      }
      \visible<2> {
        \path (0, 0) node {
          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r2.png}
        };
      }
      \visible<3> {
        \path (0, 0) node {
          \includegraphics[width=10cm]{../../experiments/misc/imgs/data_spectrum_20170409_r3.png}
        };
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Raman sidebands}
  \begin{center}
    \begin{tikzpicture}[scale=1.41176]
      \visible<1> {
        \path (0, 0) node {
          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1_before.png}
        };
        \draw[red, <-, line width=1.5] (-3.15, 0.5) -- (-2.95, 1.2)
        node[above right] {\Large 1st order heating};
        \draw[<-, line width=1.5] (-2.45, 0.2) -- (-2.25, 0.8) node[above right] {\Large Carrier};
        \draw[black!40!green, <-, line width=1.5] (-1.7, 0.2) -- (-1.55, 0.6)
        node[right] {\Large 1st order cooling};
        \draw[blue, <-, line width=1.5] (-0.95, -0.1) -- (-0.55, 0.1)
        node[right] {\Large 2nd order cooling};
        \path[magenta] (0.25, -0.5) node[right] {\Large And higher orders{$\cdots$}};
      }
      \visible<2-> {
        \path (0, 0) node {
          \includegraphics[width=12cm]{../../experiments/misc/imgs/data_spectrum_20170409_a1.png}
        };
      }
      \visible<3-> {
        \fill[white,opacity=0.95] (-4.2, -2.5) rectangle (5, 2.5);
        \path (0, 1) node[align=center]
        {
          \begin{tabular}{|c|c|}
            \hline
            \textbf{Axis}&\textbf{Ground state probability}\\\hline
            1 (Axial)&93.1(2.5)\%\\\hline
            2 (Radial)&91.9(2.3)\%\\\hline
            3 (Radial)&92.9(2.5)\%\\\hline
          \end{tabular}
        };
        \visible<4-> {
          \path (0, -1) node[align=center]
          {
            \textbf{3D ground state:} $79.5(3.6)\%$\\
            \textbf{Loss after cooling:} $15\%$\\\\
            \textbf{Total 3D ground state preparation fidelity:} $67.6(3.1)\%$
          };
        }
      }
    \end{tikzpicture}
  \end{center}
\end{frame}

\begin{frame}{Rabi flopping (radial)}
  \begin{center}
    \visible<+->{
      \includegraphics[width=10cm]{../../experiments/rabi_flop/imgs/fit_20170409_r2_0_ba.png}\\
    }
    \visible<+->{
      Good agreement in ground state probability between spectrum and Rabi flopping data.
    }
  \end{center}
\end{frame}

\begin{frame}{Rabi flopping (axial)}
  \begin{center}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_0_nol.png}
    \includegraphics[height=4.8cm]{../../experiments/rabi_flop/imgs/fit_20170409_a1_p1_nol.png}
  \end{center}
\end{frame}
